\documentclass{article}

% generate random texts
\usepackage{lipsum}

% suppress page numbering
\pagenumbering{gobble}

% set margin to 0.5in
\usepackage[
	height=9in,      % height of the text block
	width=7.5in,       % width of the text block
	top=110pt,        % distance of the text block from the top of the page
	headheight=100pt, % height for the header block
	headsep=15pt,    % distance from the header block to the text block
	heightrounded,   % ensure an integer number of lines
%	showframe,
	nofoot
	]{geometry}

% change font
\usepackage{fontspec}
\setmainfont{EB Garamond}

% affiliations
\title{resume}
\author{Yuchen Zhang}
\date{\today}

% header
\usepackage{fancyhdr} % fancy header
\usepackage{hyperref} % clickable email and phone numbers
\usepackage{fontawesome5} % icons
\usepackage[dvipsnames]{xcolor} % icon colors
\pagestyle{fancy}
\fancyhf{} % clear all fields

\fancyhead[L]{
	% name
	\textbf{\Huge Yuchen Zhang} \\ \medskip
	% email
	{\color{Cerulean} \faIcon{envelope-open-text}} \enskip
	\href{mailto:anthonyucla@ucla.edu}{\nolinkurl{anthonyucla@ucla.edu}} \\ \smallskip
	% phone
	{\color{Cerulean} \faIcon{phone}} \enskip \href{tel:13238688380}{(323) 868-8380} \\ \smallskip
	% linedin profile
	{\color{Cerulean} \faIcon{linkedin}} \enskip \href{https://www.linkedin.com/in/anthonyive}{www.linkedin.com/in/anthonyive}
}
\renewcommand{\headrulewidth}{0pt}

% Cpp logo
\newcommand{\CC}{C\nolinebreak\hspace{-.05em}\raisebox{.4ex}{\tiny\bf}\nolinebreak\hspace{-.10em}\raisebox{.4ex}{\big \bf +}}
\def\CC{{C\nolinebreak[4]\hspace{-.05em}\raisebox{.4ex}{\tiny\bf ++}}}

% vertical spaces
\newcommand{\insertvspace}{%
	\rlap{\color{white}\rule{.4pt}{.7\baselineskip}}% Mark location
	\vspace{\baselineskip}}% Insert \vspace

% More packages
\usepackage{tikz}
\usepackage{enumitem}

\begin{document}
	% define some colors
	\definecolor{VibrantBlue}{RGB}{60,140,200}
	\definecolor{progressbarbg}{rgb}{0.9, 0.9, 0.9}
	
	% section macro
	\newcommand*\circled[4]{\tikz[baseline=(char.base)]{
			\node[shape=circle, fill=#2, draw=#3, line width=2pt, text=#4, inner sep=3pt] (char) {#1};}}
	\newcommand{\ressec}[2]{
		\section*{{\small \circled{{\color{White} \faIcon{#2}}}{Cerulean}{VibrantBlue}{red}} #1}}{}
	
	% date range redefine
	\newcommand{\daterange}[2]{{\color{Cerulean} #1 -- #2}}
	
	%%%%% Education %%%%%
	
	\ressec{Education}{university}
	\begin{itemize}[leftmargin=*]
		\item[]
		\textbf{University of Southern California} \hfill \daterange{Aug. 2020}{Present} \\
		\textit{Applied Data Science} 
		
		\item[]
		\textbf{University of California, Los Angeles} \hfill \daterange{Aug. 2018}{Aug. 2020} \\
		\textit{Bachelor's Degree in Applied Mathematics, Minor in Statistics} 
		
		\item[]
		\textbf{University of Southern California}  \hfill \daterange{Aug. 2016}{July. 2017} \\
		\textit{Associate Degree in Mathematics}
	\end{itemize}

	%%%%% Work Experience and Skills %%%%%
	
	\insertvspace
	\noindent
	\begin{minipage}[t]{0.5\textwidth}
		\ressec{Work Experience}{briefcase}
		
		\begin{itemize}[leftmargin=*]
			\item[]
			\textbf{Supplemental Instruction Coach}, \textit{East Los Angeles College}, Monterey Park, CA \\
			\daterange{Aug. 2017}{Jun. 2018} \\
			SI Coach is an outstanding student who is selected and trained to conduct weekly sessions and has office hours designed to empower students' study skills. Coaching students how to become independent learners, and how to use different approach to solve problems.
			
			\item[] 
			\textbf{BUILD PODER program tutor}, \textit{East Los Angeles College}, Monterey Park, CA \\
			\daterange{Sept. 2017}{Nov. 2017} \\
			BUILD PODER is an undergraduate training program at CSU. I was one-to-one tutoring Calculus and improving the learning skills for the student in this program.
		\end{itemize}
	\end{minipage}\hspace{0.3in}  % <--- space
	\begin{minipage}[t]{0.45\textwidth}
		\ressec{Skills}{list}
		\begin{itemize}[leftmargin=*]
			\item[] 
			R \\
			\begin{tikzpicture}
				\draw[fill=progressbarbg] (0,0) -- (8,0) -- (8,0.2) -- (0,0.2) -- cycle;
				\shade[left color=Cerulean,right color=RoyalBlue] (0,0) rectangle (7.2,0.2);
			\end{tikzpicture}
		
			\item[] 
			Python \\
			\begin{tikzpicture}
				\draw[fill=progressbarbg] (0,0) -- (8,0) -- (8,0.2) -- (0,0.2) -- cycle;
				\shade[left color=Cerulean,right color=RoyalBlue] (0,0) rectangle (7.2,0.2);
			\end{tikzpicture}
		
			\item[] 
			\LaTeX \\
			\begin{tikzpicture}
				\draw[fill=progressbarbg] (0,0) -- (8,0) -- (8,0.2) -- (0,0.2) -- cycle;
				\shade[left color=Cerulean,right color=RoyalBlue] (0,0) rectangle (5,0.2);
			\end{tikzpicture}
		
			\item[] 
			\CC \\
			\begin{tikzpicture}
				\draw[fill=progressbarbg] (0,0) -- (8,0) -- (8,0.2) -- (0,0.2) -- cycle;
				\shade[left color=Cerulean,right color=RoyalBlue] (0,0) rectangle (4.5,0.2);
			\end{tikzpicture}
		
			\item[]
			Basic understanding on Bash, Zsh, Assembly Language (AT\&T style), C, and Emacs Lisp.
		\end{itemize}
	\end{minipage}

	%%%%% Internship Experience and Involvement %%%%%

	\insertvspace
	\noindent
	\begin{minipage}[t]{0.5\textwidth}		
		\ressec{Internship Experience}{handshake}
		\begin{itemize}[leftmargin=*]
			\item[]
			\textbf{Emergency Data Relief Internship}, \textit{BroadStreet} \\
			\daterange{Sept. 2020}{Present} \\
			The Primary Data Goal is to create and maintain a research-ready dataset around COVID-19 cases and deaths for every county in the nation.
			
			\item[] 
			\textbf{Internship}, \textit{Beijing Mankai Tech LLC.}, Beijing, China\\
			\daterange{July. 2019}{Aug. 2019} \\
			Analyze data of financial statements, design and optimize statement template, and other miscellaneous assignments from my employer.
		\end{itemize}
	\end{minipage}\hspace{0.3in}  % <--- space
	\begin{minipage}[t]{0.45\textwidth}
		\ressec{Involvement}{cube}
		\begin{itemize}[leftmargin=*]
			\item[] 
			\textbf{ISAP Publicity Director}, \textit{East Los Angeles College}, Monterey Park, CA \\
			Pub​lic​ity Di​rec​tor of In​ter​na​tional Stu​dent Ad​vance​ment Pro​‐ gram(ISAP), di​rected 2017 Lunar New Year Fair, Food sales, UCSD-UCI, and varies pub​lic​ity ac​tiv​i​ties.
		\end{itemize}
	\end{minipage}

	%%%%% Academic Projects and Miscellaneous %%%%%

	\insertvspace
	\noindent
	\begin{minipage}[t]{0.5\textwidth}
		\ressec{Academic Projects}{project-diagram}
		\begin{itemize}[leftmargin=*]
			\item[] 
			\textbf{\LaTeX\ Writing Style of ArXiV Authors} \\
			{\color{Cerulean} \href{https://github.com/Anthonyive/machine-learning-project.git}{https://github.com/Anthonyive/machine-learning-project.git}} \\
			The idea of this project is to cluster writing styles of different authors across different categories in \href{https://arxiv.org}{arXiv.org}'s Math topic. Team member and I downloaded source files across categories, web scrapped data for each paper, and generated CSVs. The end result was clustered by k-means algorithm.
		\end{itemize}
	\end{minipage}\hspace{0.3in}  % <--- space
	\begin{minipage}[t]{0.45\textwidth}
		\ressec{Miscellaneous}{bullseye}
		\begin{itemize}[leftmargin=*]
			\item 
			Interested in leather crafting, wood working, video games, ping pong, and more!
			\item
			Bilingual in Chinese and English (oral and written translation).
			\item
			Certified American Red Cross Adult and Pediatric First Aid/CPR/AED.
		\end{itemize}
	\end{minipage}
	
\end{document}