\documentclass{article}

% generate random texts
\usepackage{lipsum}

% suppress page numbering
\pagenumbering{gobble}

% spacing between sections
\usepackage{titlesec}
\titlespacing{\section}{0pt}{\parskip}{-\parskip}
\titlespacing{\subsection}{0pt}{\parskip}{-\parskip}
\titlespacing{\subsubsection}{0pt}{\parskip}{-\parskip}

% set margin to 0.5in
\usepackage[
	height=9in,      % height of the text block
	width=7.5in,       % width of the text block
	top=90pt,        % distance of the text block from the top of the page
	headheight=100pt, % height for the header block
	headsep=15pt,    % distance from the header block to the text block
	heightrounded,   % ensure an integer number of lines
%	showframe,
	nofoot
	]{geometry}

% change font
\usepackage{fontspec}
\setmainfont{EB Garamond}

% affiliations
\title{resume}
\author{Yuchen Zhang}
\date{\today}

% header
\usepackage{fancyhdr} % fancy header
\usepackage{hyperref} % clickable email and phone numbers
\usepackage{fontawesome5} % icons
\usepackage[dvipsnames]{xcolor} % icon colors
\pagestyle{fancy}
\fancyhf{} % clear all fields

% color
\usepackage{xcolor}
\definecolor{apple-blue}{RGB}{0,122,255}
\definecolor{apple-teal}{RGB}{90,200,250}
\definecolor{apple-green}{RGB}{52,199,89}
\definecolor{linkedin-blue}{RGB}{0,119,181}
\definecolor{github-black}{RGB}{31,31,31}

\newcommand\myshade{85}
\colorlet{myurlcolor}{apple-blue}

\hypersetup{
	urlcolor   = myurlcolor!\myshade!black,
	colorlinks = true,
}


\fancyhead[L]{
	% name
	\textbf{\Huge Yuchen Zhang} \\ \medskip
	% address
	\colorlet{myurlcolor}{apple-teal}
	\hypersetup{urlcolor=myurlcolor!\myshade!black,colorlinks = true}
	{\color{apple-teal} \faIcon{house-user}} \enskip
	\href{https://www.google.com/maps?q=1977+Lupine+Ave,+CA,+91755}{1977 Lupine Ave, Monterey Park, CA} \hfill
	% email
	\colorlet{myurlcolor}{apple-blue}
	\hypersetup{urlcolor=myurlcolor!\myshade!black,colorlinks = true}
	\urlstyle{same}
	{\color{apple-blue} \faIcon{inbox}} \enskip
	\href{mailto:anthonyucla@ucla.edu}{\nolinkurl{anthonyucla@ucla.edu}} \hfill
	% phone
	\colorlet{myurlcolor}{apple-green}
	\hypersetup{urlcolor=myurlcolor!\myshade!black,colorlinks = true}
	{\color{apple-green} \faIcon{phone}} \enskip \href{tel:13238688380}{(323) 868-8380} \hfill
	% linedin profile
	\colorlet{myurlcolor}{linkedin-blue}
	\hypersetup{urlcolor=myurlcolor!\myshade!black,colorlinks = true}
	{\color{linkedin-blue} \faIcon{linkedin}} \enskip \href{https://www.linkedin.com/in/anthonyive}{www.linkedin.com/in/anthonyive}
}
\renewcommand{\headrulewidth}{0pt}

% Cpp logo
\usepackage{relsize}
\newcommand\CC{C\nolinebreak[4]\hspace{-.05em}\raisebox{.4ex}{\relsize{-3}{\textbf{++}}}}

% horizontal separator
\newcommand{\divider}{\vskip2pt\hrule\vskip2pt}
\setlength{\parindent}{0pt}

% vertical spaces
\newcommand{\insertvspace}{%
	\rlap{\color{white}\rule{.4pt}{.7\baselineskip}}% Mark location
	\vspace{\baselineskip}}% Insert \vspace

% More packages
\usepackage{tikz}
\usepackage{enumitem}

\begin{document}
	\section*{EDUCATION}
	\divider
		\subsection*{University of Southern California \hfill {\normalfont Los Angeles, CA}}
		\noindent
		Viterbi School of Engineering \hfill August 2020 \\
		Master of Science, Applied Data Science \hfill GPA N/A \\
		
		\subsection*{University of California, Los Angeles \hfill {\normalfont Los Angeles, CA}}
		\noindent
		College of Letters and Science \hfill August 2018 \\
		Bachelor of Science, Applied Mathematics \hfill GPA 3.863 \\
		
	\section*{SKILLS}
	\divider
	\begin{itemize}
		\setlength\itemsep{-1pt}
		\item Programming Languages: Python, R, \LaTeX, UNIX Shell, C, \CC, Assembly Language (AT\&T style), and Emacs Lisp
		\item Database Management: SQL
		\item Tools: GitHub, RStudio, Tensorflow, Pandas, Numpy, MATLAB, Latex, DrawIo, Photoshop.
	\end{itemize}
		
	\section*{WORK EXPERIENCE}
	\divider
		\subsection*{BroadStreet{\normalfont, Remote \hfill Sept. 2020 - Present}}
			\subsubsection*{Emergency Data Relief Internship, QA track}
			\begin{itemize}
				\setlength\itemsep{-1pt}
				\item In charge of quality assurance track for daily number of COVID-19 cases. 
				\item Automate quality assurance process using Google Sheet API and pandas
				\item Fix trend breaks, correct input errors, and communicate with team members.
			\end{itemize}
		
		
		\subsection*{Beijing Mankai Tech LLC.{\normalfont, Beijing, China \hfill Summer 2019}}
		\subsubsection*{Data Analyst Internship}
		\begin{itemize}
			\item Analyzed data of financial statements, designed and optimized statement template.
		\end{itemize}
	
		\subsection*{East Los Angeles College{\normalfont, Monterey Park, CA \hfill Aug. 2017 – Jun. 2018}}
		\subsubsection*{Supplemental Instruction Coach}
		\begin{itemize}
			\setlength\itemsep{-1pt}
			\item Attended professors' classes, listened to students' needs, and designed teaching plans.
			\item Formed study sessions, helped students' questions, and assigned extra practice problems.
		\end{itemize}
	
	\section*{PROJECT EXPERIENCE}
	\divider
	
	\colorlet{myurlcolor}{github-black}
	\hypersetup{urlcolor=myurlcolor!\myshade!black,colorlinks = true}
	
		\subsection*{Title: Mapping Uncanny Valley (Ongoing) \hfill {\normalfont Spet. 2020 - Present}}
		\noindent
		\href{https://github.com/Anthonyive/Research-Mapping-Uncanny-Valley.git}{\faIcon{github}} The aim of this project was to help answer what makes text creepy.
		\begin{itemize}
			\setlength\itemsep{-1pt}
			\item Quantized text posts on reddit (r/NoSleep and r/Confessions) 
			\item Word and sentence embeddings using word2vec, fasttext, and \href{https://arxiv.org/abs/1908.10084}{Sentence-BERT}
			\item GPU acceleration for spaCy NLP and tensorflow ANN.
		\end{itemize}
	
		\subsection*{Title: Research on LATEX Writing Style of arXiv Authors \hfill {\normalfont Summer 2020}}
		\noindent
		\href{https://github.com/Anthonyive/machine-learning-project.git}{\faIcon{github}} The aim of this project was to cluster writing styles of different authors in \href{https://arxiv.org}{arXiv.org}’s Math topic. 
		\begin{itemize}
			\setlength\itemsep{-1pt}
			\item Web scrapped source files and .tex files of papers in Math topic using R
			\item Text filtering using regex and tallied commands, environments, and packages usage using Python
		\end{itemize}
	
	\section*{LEADERSHIP}
	\divider
	\subsection*{International Student Advancement Program{\normalfont, East Los Angeles College \hfill 2016 - 2017}}
	\subsubsection*{Publicity Director}
	\begin{itemize}
		\setlength\itemsep{-1pt}
		\item Designed and printed high quality minimal fliers for Food Sales, Lunar Festival, New Year Fair, and more club activities.
		\item Communicated and collaborated with teammates to help and decorate club activities.
	\end{itemize}
	
	
\end{document}